The Freeplay Sandbox: a Novel Methodology for the Evaluation of Social Robotics

### 2017-10-05 paper.tex
Update on Overleaf.

To mitigate the technical challenges presented by free play interactions in
their most unconstrained version (like high dimensionality and uncertainties),
we have developed a \emph{free play sandbox}, Figure~\ref{fig|setup}: a large
touchscreen (60cm $\times$ 33cm) is used as an interactive surface
(\emph{sandtray} paradigm~\cite{baxter2012touchscreen}). Two agents (either a
pair of children or one child and one robot) play together by freely moving on a
2D plane items (characters and blocks, see Figure~\ref{fig|sandbox}). A
background image depicts a generic empty environment, with different symbolic
zones (water, grass, path, bushes...). Additionally, the children can draw on
the background using a tool applying a color on their touches. The players do
not have any particular task to complete, they are simply invited to freely
play.

@@

observing and quantifying social interactions.

@@

Depending of the focus of the study, two modes of control for the robot are
available. If the interest is on evaluating a specific robot behaviour, the
robot can be autonomously controlled using inputs from the different sensors.
This setup allows to explore the impact of different social behaviours on the
children in an open yet standardised environment.

@@

Standardised method to gather data and use deep learning for automated
annotation.

Can be used to explore the impact of social behaviours of the robot: "game
action policy" can be identical, but more social behaviours can be desired

Can be used to explore learning of social action policy for a robot.

@@

A detailed description of the dataset is outside of the scope of this paper, and
we only provide hereafter cursory informations on the dataset. Specific details
regarding the methodology and the acquisition procedure can be found on the
dataset website: [hidden for blind review]. The dataset is open and accessible
to any interested researcher.

>>>>

To mitigate the technical challenges presented by free play interactions in
their most unconstrained version (like high dimensionality and uncertainties),
we have developed a \emph{free play sandbox}, Figure~\ref{fig|freeplay}: a large
touchscreen (60cm $\times$ 33cm) is used as an interactive surface
(\emph{sandtray} paradigm~\cite{baxter2012touchscreen}). Two agents (either a
pair of children or one child and one robot) play together by freely moving on a
2D plane items (characters and blocks, see Figure~\ref{fig|sandbox}). A
background image depicts a generic empty environment, with different symbolic
zones (water, grass, path, bushes...). Additionally, the children can draw on
the background using a tool applying a color on their touches. The players do
not have any particular task to complete, they are simply invited to freely
play.

@@

The Freeplay Sandbox provides the opportunity to observe children interacting in a natural way in an open but framed setup. As the system can run on a single computer platform it can easily be deployed in the 'wild', in places where the children naturally interact such as classroom. The quantity and thoughtfulness of information logged allows to keep a track of every interaction happening around the game.

These advantages combined with the openness of the task proposed make this setup a powerful tool to observe and quantify a large spectrum of social behaviours expressed by children when interacting in a natural environment (might be interesting to add a list here). The compactness of the system makes it easy to compare data from different locations.

@@

Depending of the focus of the study, two modes of control for the robot are
available. If the interest is on evaluating a specific robot behaviour, the
robot can be autonomously controlled using inputs from the different sensors.
This setup allows to explore the impact of different social behaviours on the
children independently of the 'game policy' controlling by the robot.

@@

With the quantity of data logged and the high number of interaction achievable with the Freeplay Sandbox, it supports the type of requirement for recent Machine Learning approaches such as deep learning. The similar position of the children in all interactions makes the combination of data from different interaction easier than other less compact systems.

From the information collected on the children, social behaviours can be extracted and used on a robot.

@@

A detailed description of the dataset is outside of the scope of this paper, and
we only provide hereafter cursory informations on the dataset. Specific details
regarding the methodology and the acquisition procedure can be found on the
dataset website: [hidden for blind review]. The dataset is open and accessible
to any interested researcher.
\todo{Probably add "an anonymised version of the dataser is open..." Reviewers might be concerned about ethics}
